\thetitle

### 2020-11-21 writing/results.tex
small edit in results

A second point of interest is that the exceptions of
the erasure semantics either help the rational programmer immediately or 
the rational programmer fails to debug a scenario altogether (in red). This shouldn't
come as a surprise; no matter how many type annotations the programmer
adds to an erasure program, if the type checker doesn't reject the
program, running the program produces always the same outcome. Thus an
exception from the erasure's runtime has to point to the buggy component with
the first try. Otherwise the rational programmer types an irrelevant
component, runs the program again and the exception points again to the
already typed component.

A third interesting piece of information from
the figure is that every mode has failed debugging scenarios. This should
not come as a surprise to the astute
reader After all, as we
discuss above, some modes are more successful than others in certain
scenarios. Indeed any mode can fail if running a scenario results in an
exception and the exception carries no useful information about which
component the programmer should type next, e.g., because the stack trace 
does not contain frames from the component of the program.
This explains the majority of
failures to debug failed scenarios but not all. The next section takes a
closer look at these unexpected situations as part of the lessons we
extract from our experimental results.

>>>>

A second point of interest is that the exceptions of
the erasure semantics either help the rational programmer immediately or 
the rational programmer fails to debug a scenario altogether (in red). This shouldn't
come as a surprise; no matter how many type annotations the programmer
adds to an erasure program, if the type checker doesn't reject the
program, running the program produces always the same outcome. Thus an
exception from the erasure's runtime has to point to the buggy module with
the first try. Otherwise the rational programmer types an irrelevant
module, runs the program again and the exception points again to the
already typed module.

A third notable piece of information from
the figure is that every mode has failed debugging scenarios, not just
erasure. This should
not come as a surprise to the astute
reader. After all, as we
discuss above, some modes are more successful than others in certain
scenarios. Indeed any mode can fail if running a scenario results in an
exception and the exception carries no useful information about which
module the programmer should type next, e.g., because the stack trace 
does not contain frames from any module of the program. This situation
can even happen immediately, which explains failures with 0 effort. 
However  while the majority of
failures to debug failed scenarios follow this pattern, a few do not. The next section takes a
closer look at these unexpected failures of the rational programmer as part of the lessons we
extract from our experimental results.
